Resolvable Ambiguity

### 2019-07-05 paper/paper.tex
Clean up and make resolvability problems more formal

\begin{definition}
  A word $w \in L(\T, T, \parse)$ is ambiguous, written $\amb(w)$, iff

@@

\begin{definition}\label{def:resolvable-word}
  A word $w \in L(\T, T, \parse)$ is resolvably ambiguous, written $\rho_{\Sigma}(w, \parse)$, iff

@@

For clarity we abbreviate $\rho_{\T}(w, \parse)$ as $\rho(w)$ if $\T$
and $\parse$ are clear from the context.

@@

  $\forall w \in L(\T, T, \parse).\ \rho_{\T}(w, \parse)$.
\end{definition}

@@

\begin{description}
\item[Static resolvability.] Given a language defined by $\parse$, determine if it is resolvably ambiguous.
\item[Dynamic resolvability.] Given a language defined by $\parse$ and a word $w$ such that $\parse(w) \neq \emptyset$, determine if $w$ is resolvably ambiguous.
\end{description}

>>>>

\begin{definition}
  A word $w \in L(\T, T, \parse)$ is ambiguous, written $\amb_L(w)$, iff

@@

\begin{definition}\label{def:resolvable-word}
  A word $w \in L(\T, T, \parse)$ is resolvably ambiguous, written $\rho_L(w)$, iff

@@

@@

  $\forall w \in L(\T, T, \parse).\ \rho_L(w)$.
\end{definition}

@@

\begin{description}
\item[Static resolvability.] Given a language $L(\T, T, \parse)$, determine whether $\rho(L)$.
\item[Dynamic resolvability.] Given a word $w \in L(\T, T, \parse)$, determine whether $\rho_L(w)$.
\end{description}
